---
title: "Ryan"
author: "Ryan Crawford"
date: "2/28/2021"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

* I am a technician who works at the amazingly-named Cornell University College of Agriculture and Life Sciences School of Integrative Plant Science Plant Breeding and Genetics Section--CUCALSSIPSPBG, for short.

* I have two kids, 5 years and 15 months old.

* I say that I like to read for pleasure but it takes me forever to finish anything. 

![This is the book I'm slooooowly reading:](https://external-content.duckduckgo.com/iu/?u=https%3A%2F%2Ftse1.mm.bing.net%2Fth%3Fid%3DOIP.JGPUVujQao6J7g5-RQ96oQHaLR%26pid%3DApi&f=1 width="150px"></right>)

</br>

### Finally, a little bit of iris data

```{r}
knitr::kable(iris %>% group_by(Species) %>% summarize_all(mean))
```
### And an iris plot: 
```{r}
iris %>% 
  ggplot(., aes(x=Sepal.Length, y=Sepal.Width, color=Species))+
  geom_point()+
  theme_bw()+
  geom_smooth(method="lm", se=F)
```


